Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-12 inc/introduction.tex
tweak introduction

In Chapter \ref{chap:ms_model} I will introduce the of the work of Michalik and Sipe~\cite{michalik_analytic_2006,michalik_erratum:_2008}, describing electron bunch propagation in an mean-field self-similar Analytic Gaussian (AG) pulse treatment.
For free-space propagation, the AG model of charge bunch dynamics has already been shown to be very consistent with full Monte Carlo (i.e., particle tracking) simulations for a wide variety of electron pulse shapes~\cite{michalik_analytic_2006,michalik_evolution_2009}, including the uniform ellipsoid~\cite{luiten_how_2004}.
Due primarily to the versatility of the AG model which results from its use of transverse and longitudinal pulse position and momentum variances, the AG approach is applicable to both the single electron per pulse limit~\cite{lobastov_four-dimensional_2005}, where momentum variances determine the pulse evolution and the model is exact (obeying Gaussian optics), and the high charge density limit in which space-charge effects dominate~\cite{luiten_how_2004,siwick_ultrafast_2002,cao_femtosecond_2003}.
 to include the influence of linear external forces due to electron optical elements.
In Chapter \ref{chap:extension}, I present some optimizations to the AG model, and develop useful initial conditions representing single-photon photoemission from a typical metal photocathode.
I then present my extensions to the Michalik and Sipe AG model which permit the inclusion of generic external forces.
In order to adapt this extended AG model for simulating pulses in a realistic UEM column, I then present specific contributions that arise from magnetic lenses, RF cavities and DC accelerators.
The resulting computationally efficient propagation analysis can then be used to model, and hence design, UEM columns and UED systems in a straightforward manner.
I would like to note that the analyses presented are performed in the non-relativistic limit, which is a reasonable approximation for the typical 20-200keV electron energies employed in UED and electron microscopy.

@@

All of these considerations motivate the construction of the prototype UEM column being built by our group at UIC.
In Chapter \ref{chap:prototype}, I detail the design and fabrication of large-aperture electron-optical elements, which can readily admit these large width electron pulses; included among these are the accelerator and magnetic lenses.
Then, before I conclude, I will in Chapter \ref{chap:photocathode} highlight the photocathode engineering work which has been undertaken in an attempt to reduce the rms transverse momentum.
I will present several different photoemission processes, some of which are yielding very promising results.
In fact, our recent work may even challenge our current understanding of photoemission.

>>>>

In Chapter \ref{chap:ms_model}, I will introduce the of the work of Michalik and Sipe~\cite{michalik_analytic_2006,michalik_erratum:_2008}, describing free-space electron bunch propagation in an mean-field self-similar Analytic Gaussian (AG) pulse treatment.
For free-space propagation, the AG model of charge bunch dynamics has already been shown to be very consistent with full Monte Carlo (i.e., particle tracking) simulations for a wide variety of electron pulse shapes~\cite{michalik_analytic_2006,michalik_evolution_2009}, including the uniform ellipsoid~\cite{luiten_how_2004}.
Due primarily to the versatility of the AG model which results from its use of transverse and longitudinal pulse position and momentum variances, the AG approach is applicable to both the single electron per pulse limit~\cite{lobastov_four-dimensional_2005}, where momentum variances determine the pulse evolution and the model is exact (obeying Gaussian optics), and the high charge density limit in which space-charge effects dominate~\cite{luiten_how_2004,siwick_ultrafast_2002,cao_femtosecond_2003}.
Unfortunately, the model lacks the ability to model the dynamics of electron pulses under influence of external forces; this prevents the AG model from being used to simulate the behavior of electron pulses in realistic microscope columns.
Additionally, to be useful for UEM, for which initial pulse conditions are of notable importance for the performance of the instrument, a realistic set of intial conditions is essential for accurately modeling the pulse dynamics.

In Chapter \ref{chap:extension}, I present some optimizations to the AG model, and develop useful initial conditions representing single-photon photoemission from a typical metal photocathode.
I then present my extensions to the Michalik and Sipe AG model which permit the inclusion of generic linear external forces, such as those due to perfect electron-optical elements in a microscope column.
In order to adapt this extended AG model for simulating pulses in a realistic UEM column, I then present specific contributions that arise from magnetic lenses, RF cavities and DC accelerators.
The resulting computationally efficient propagation analysis can then be used to model, and hence design, UEM columns and UED systems in a straightforward manner.
Note that the analyses presented are performed in the non-relativistic limit, which is a reasonable approximation for the typical 20-200keV electron energies employed in UED and electron microscopy.

@@

All of these considerations motivate the construction of the prototype UEM column being built by our group at UIC.
In Chapter \ref{chap:prototype}, I detail the design and fabrication of large-aperture electron-optical elements, which can readily admit these large width electron pulses; included among these are the accelerator and magnetic lenses.
Then, before I conclude, I will in Chapter \ref{chap:photocathode} highlight the photocathode engineering work which has been undertaken in an attempt to reduce the rms transverse momentum of the emitted electron pulses.
In fact, the search for a low transverse momentum electron source has applications beyond, UEM and UED; the fields of X-ray Free Electron Lasers (XFELs,~\cite{nemeth_high_2010}) and Compact X-ray Light Sources (CXLS) [ref] will also benefit from such a source.
I will present investigations of several different photoemission processes, some of which are yielding very promising results.
In fact, our recent work on excited-state thermionic emission~\cite{berger_excited_2012} may even challenge long-standing ideas about which materials and processes may hold the keys to low-emittance (or high-brightness) electron sources.
